### 2018-11-07 Sections/protocols_for_the_quantum_internet.tex
Restructured microwaves

Perhaps the simplest quantum information processing task is that of perfect random number generation. True random numbers have widespread applications in cryptography, Monte-Carlo simulations, and any type of randomised (e.g \textbf{BPP}\index{BPP}) algorithm.

>>>>

Perhaps the simplest quantum information processing task is that of perfect random number generation. True random numbers have widespread applications in cryptography, Monte-Carlo simulations\index{Monte-Carlo simulations}, and any type of randomised (e.g \textbf{BPP}\index{BPP}) algorithm.

### 2018-11-07 Sections/quantum_channels.tex
Restructured microwaves

\begin{figure}[!htbp]
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\hat\rho_S} & \multigate{1}{\hat{U}_{S,E}} & \qw & \,\,\,\,\,\mathcal{E}(\hat\rho_S) \\
    \lstick{\ket{0}_E} & \ghost{\hat{U}_{S,E}} & \qw & \times \\
} \nonumber
\end{align}
\captionspacefig \caption{Model for the quantum process formalism, as a system state $\hat\rho_S$ undergoing joint unitary evolution with an environment state $\ket{0}_E$, which is subsequently traced out, yielding an arbitrary quantum process $\mathcal{E}(\hat\rho_S)$ acting on the primary system.} \label{fig:q_proc}
\end{figure}

@@

Multiple consecutive processes may be composed using the notation,
\begin{align}
\mathcal{E}_n(\dots \mathcal{E}_2(\mathcal{E}_1(\hat\rho)))=(\mathcal{E}_n \circ \dots \circ \mathcal{E}_2\circ\mathcal{E}_1)(\hat\rho).
\end{align}
In general, processes do not commute, i.e \mbox{$\mathcal{E}_1\circ \mathcal{E}_2 \neq \mathcal{E}_2\circ \mathcal{E}_1$}. Unless unitary, quantum processes are irreversible, meaning that errors accumulate and cannot be overcome without the overhead of some form of quantum error correction (QEC) \cite{bib:Shor95, bib:CalderbankShor96, bib:NielsenChuang00}. The linearity of Eq.~(\ref{eq:kraus_rep}) implies that quantum processes are also linear,
\begin{align}
	\mathcal{E}(\hat\rho_1+\hat\rho_2) = \mathcal{E}(\hat\rho_1)+\mathcal{E}(\hat\rho_2).
\end{align}

>>>>

\begin{figure}[!htbp]
\begin{align}
\Qcircuit @C=1em @R=1.6em {
    \lstick{\hat\rho_S} & \multigate{1}{\hat{U}_{S,E}} & \qw & \,\,\,\,\,\mathcal{E}(\hat\rho_S) \\
    \lstick{\ket{0}_E} & \ghost{\hat{U}_{S,E}} & \qw & \times \\
} \nonumber
\end{align}
\captionspacefig \caption{Model for the quantum process formalism, as a system state $\hat\rho_S$ undergoing joint unitary evolution with an environment state $\ket{0}_E$, which is subsequently traced out, yielding an arbitrary quantum process $\mathcal{E}(\hat\rho_S)$ acting on the primary system. For the most general possible class of quantum processes to be enabled, the dimension of the environment Hilbert space must grows quadratically with the dimension of the primary Hilbert space.\index{Hilbert space}} \label{fig:q_proc}
\end{figure}

@@

Multiple consecutive processes may be composed using the notation,
\begin{align}
\mathcal{E}_n(\dots \mathcal{E}_2(\mathcal{E}_1(\hat\rho)))=(\mathcal{E}_n \circ \dots \circ \mathcal{E}_2\circ\mathcal{E}_1)(\hat\rho).
\end{align}
In general, processes do not commute, i.e \mbox{$\mathcal{E}_1\circ \mathcal{E}_2 \neq \mathcal{E}_2\circ \mathcal{E}_1$}. Unless unitary, quantum processes are irreversible, meaning that errors accumulate and cannot be overcome without the overhead of some form of quantum error correction (QEC) \cite{bib:Shor95, bib:CalderbankShor96, bib:NielsenChuang00}. The linearity of Eq.~(\ref{eq:kraus_rep}) implies that quantum processes are also linear\index{Linearity},
\begin{align}
	\mathcal{E}(\hat\rho_1+\hat\rho_2) = \mathcal{E}(\hat\rho_1)+\mathcal{E}(\hat\rho_2).
\end{align}
